Quality Criteria for SKOS Vocabularies

### 2012-03-21 criteria.tex
started structur criteria

The commonality of the following metrics is that they identify possible weaknesses when $V$ is used in scenarios exploiting the structure of its RDF graph.

\subsubsection{Loose Concepts} is a criterion motivated by the notion of ``orphan terms'' in the literature~\cite{Hedden2010}, which are are terms without any associative or hierarchical relationships. Checking for them is common in existing thesaurus development applications and also suggested by \cite{Z39.19:2005}. When we apply this to SKOS vocabularies, a loose concept is a concept that has no semantic relations with other conceptual resources and thus do not occur in any of the pairs yielded by $SR$. Although they might have attached lexical labels, they lack valuable context information that is considered essential for, e.g., search query expansion. Calculation can be done by iterating over all elements in $C$, filtering those not having a semantic relation to any other conceptual resource.

>>>>

The commonality of the following criteria is that they identify possible weaknesses when $V$ is used in scenarios exploiting the structure of its RDF graph.

\paragraph{Loose Concepts}

is a criterion motivated by the notion of ``orphan terms'' in the literature~\cite{Hedden2010}, which are are terms without any associative or hierarchical relationships. Checking for them is common in existing thesaurus development applications and also suggested by \cite{Z39.19:2005}. When we apply this to SKOS vocabularies, a loose concept is a concept that has no semantic relations with other conceptual resources and thus do not occur in any of the pairs yielded by $SR$. Although they might have attached lexical labels, they lack valuable context information that is considered essential for, e.g., search query expansion. Calculation can be done by iterating over all elements in $C$, filtering those not having a semantic relation to any other conceptual resource.
